Projection analysis to measure biological elaboration and innovation.

### 2022-03-08 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

```{r header, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE, eval = TRUE}
## Installing the dispRity package from the CRAN
install.packages("dispRity")
## Installing the mcmcmcglmmm package from github
if(!require(devtools)) install.packages("devtools")
devtools:install_github("TGuillerme/mcmcmcglmmm")
## Loading the packagges
library(mcmcmcglmmm)
library(dispRity)
```

@@

```{r, echo = FALSE, eval = FALSE}
library(mcmcmcglmmm)

## Making the parametrisation chains
parametrisation_chains <- make.mini.chains(data = charadriiformes$data,
                                           dimensions = c("PC1", "PC2", "PC3"),
                                           randoms = c("global", "clade"),
                                           residuals = "global",
                                           tree = charadriiformes$tree,
                                           parameters = list(nitt = 50000, burnin = 0, thin = 500))

>>>>

```{r header, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE, eval = FALSE}
## Installing the dispRity package from the CRAN
install.packages("dispRity")
## Installing the mcmcmcglmmm package from github
if(!require(devtools)) install.packages("devtools")
devtools::install_github("TGuillerme/mcmcmcglmmm")
```

```{r, echo = TRUE, results = 'hide', message = FALSE, warning = FALSE, eval = TRUE}
## Loading the packagges
library(mcmcmcglmmm)
library(dispRity)
```

@@

```{r, echo = FALSE, eval = FALSE, eval = TRUE}
## Making the parametrisation chains
parametrisation_chains <- make.mini.chains(data = charadriiformes$data,
                                           dimensions = c("PC1", "PC2", "PC3"),
                                           randoms = c("global", "clade"),
                                           residuals = "global",
                                           tree = charadriiformes$tree,
                                           parameters = list(nitt = 50000, burnin = 0, thin = 500))
